Transcriptomic Analysis of Expressions of Ten genes and Their Prognostic Value in Head and Neck Squamous Cell Carcinoma

### 2021-05-09 Cover_letter_JPM.tex
Updates from Overleaf

***[latex line 410]
In line 154 paragraph, what does "unclean data" mean, missing values or zero expression? 
=> First, although \acrshort{tcga} genomics data was harmonized, there is unclean data, including null expressed genes, over 50\% of the cohort, should be manually investigated and cleaned. 
After detailed 梳理, we found that the number of protein-coding genes in the TCGA RNA-Seq dataset should be corrected  (20499 -> 20500)
The three challenges are not “challenges” at all. The authors exaggerated the difficulties here. 不要誇大說明 謙虛道歉，修改說法

The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it was shown here in the following paragraph.
%%%
=>  However, there are three steps of biomarker discovery from survival analysis.
***=> Third, we need to find an optimal cutpoint of that \acrshort{rna} expression data to maximize candidate mining coverage. 這個 要改為 reviewer's comment (risk of maximizing P-value with cutoff scan)
...

>>>>

***[latex line 410]
In line 154 paragraph, what does "unclean data" mean, missing values or zero expression? 
=> First, although \acrshort{tcga} genomics data was harmonized, there is unclean data, including null expressed genes, over 50\% of the cohort, should be manually investigated and cleaned. 
After extended organizing, we found that the number of protein-coding genes in the TCGA RNA-Seq dataset should be corrected  (20499 -> 20500).
%% The three challenges are not "challenges" at all. The authors exaggerated the difficulties here. 
%不要誇大說明 謙虛道歉，修改說法
=> We are apology for exaggerating the difficulties of our workflow.
The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it was shown here in the following two paragraphs.

%%%
There are three steps of biomarker discovery from survival analysis.
First, although \acrshort{tcga} genomics data was harmonized, there is unclean data, including null expressed genes, over 50\% of the cohort, should be manually investigated and cleaned.
%%% *** with more
Second, we find a way to determine candidates from the expression level of 20,500 human protein-coding genes\cite{Clamp2007}.

% risk of 
Third, we try to find an optimal cutpoint of that \acrshort{rna} expression data to maximize candidate mining coverage.
However, this strategy might identify more weak "biomarkers". Thus, the false positives and adjustment of multiple comparison should be corrected by \acrfull{fdr}.

### 2021-05-09 main.tex
Updates from Overleaf

In summary, identifying predictive biomarkers for selecting standard-of-care or advanced systemic therapy\cite{Cristina2019} in \acrshort{hnscc} is crucial. 
However, there are three challenges of biomarker discovery from survival analysis.
First, although \acrshort{tcga} genomics data was harmonized, there is unclean data, including null expressed genes, over 50\% of the cohort, should be manually investigated and cleaned.
Second, we need to find a way to determine candidates from the expression level of 20,500 human protein-coding genes\cite{Clamp2007}. Usually, the investigators should get the rationale or revelation of the genes of interest on a specific cancer type. They should upload those genes manually onto bioinformatics tools, such as SurvExpress (http://bioinformatica.mty.itesm.mx:8080/Biomatec/ \newline
SurvivaX.jsp\cite{Aguirre-Gamboa2013}, which has been lost since Oct/2019 and currently out of funds), and analyze the cohort (e.x. \acrshort{tcga}). After downloading the survival results, they could curate plots and tables carefully.
It is not possible to scan the whole human protein-coding genome in this way.
Third, we need to find an optimal cutpoint of that \acrshort{rna} expression data to maximize candidate mining coverage. The above mentioned web-based tools might set a cutpoint at the median, 1/4 quantile, or 3/4 quantile for subsequent analyses. There are several visualization software or R packages which deal with cutoff determination, such as Prognoscan\cite{Mizuno2009a}, Cutoff Finder\cite{Budczies2012}, Findcut\cite{Chang2017a}, Human protein atlas\cite{Uhlen2017}, OptimalCutpoints\cite{Cristina2019},  cutpointr (available at https://github.com/thie1e/cutpointr), and cutoffR (available at https://cran.r-project.org/web/
packages/cutoffR). However, non of them could combine the scanning of the protein-coding genes and cutoff optimization programmatically.

>>>>

%%% ***
In summary, identifying predictive biomarkers for selecting standard-of-care or advanced systemic therapy\cite{Cristina2019} in \acrshort{hnscc} is crucial.
\begin{MyColorPar}{red} %%%
There are three steps of biomarker discovery from survival analysis.
First, although \acrshort{tcga} genomics data was harmonized, there is unclean data, including null expressed genes, over 50\% of the cohort, should be manually investigated and cleaned.
%%% *** with more
Second, we find a way to determine candidates from the expression level of 20,500 human protein-coding genes\cite{Clamp2007}.
\end{MyColorPar} %%%
Usually, the investigators should get the rationale or revelation of the genes of interest on a specific cancer type. They should upload those genes manually onto bioinformatics tools, such as SurvExpress (http://bioinformatica.mty.itesm.mx:8080/Biomatec/ \newline
SurvivaX.jsp\cite{Aguirre-Gamboa2013}, which has been lost since Oct/2019 and currently out of funds), and analyze the cohort (e.x. \acrshort{tcga}). After downloading the survival results, they could curate plots and tables carefully.
It is not possible to scan the whole human protein-coding genome in this way.
\begin{MyColorPar}{red} %%% %%%
% risk of 
Third, we try to find an optimal cutpoint of that \acrshort{rna} expression data to maximize candidate mining coverage.
However, this strategy might identify more weak "biomarkers". Thus, the false positives and adjustment of multiple comparison should be corrected by \acrfull{fdr}.
%Exploring all possible expression cutoffs is controversial. A robust expression biomarker should be effective and detectable at most major cutoffs. 
%Compared to a fixed quantile cutoff, a sliding window cutoff selection of cutoffs would capture more genes whose p-values just reach the significant level (p=0.05). For example, a gene with a p-value of 0.1 at 25\% or 50\% quantile cutoff could achieve a p-value of 0.04 at 70\% quantile cutoff. But it is not expected that a gene with a p-value of 0.1 at 25\% or 50\% quantile cutoff could achieve a p-value of 1e-5 at 70\% quantile cutoff. 
\end{MyColorPar} %%%
The above mentioned web-based tools might set a cutpoint at the median, 1/4 quantile, or 3/4 quantile for subsequent analyses. There are several visualization software or R packages which deal with cutoff determination, such as Prognoscan\cite{Mizuno2009a}, Cutoff Finder\cite{Budczies2012}, Findcut\cite{Chang2017a}, Human protein atlas\cite{Uhlen2017}, OptimalCutpoints\cite{Cristina2019},  cutpointr (available at https://github.com/thie1e/cutpointr), and cutoffR (available at https://cran.r-project.org/web/
packages/cutoffR). However, non of them could combine the scanning of the protein-coding genes and cutoff optimization programmatically.
